---
title: "Homework 3"
author: "Ryan Ackerman"
date: "6/7/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())

library(ggplot2)
library(lubridate)
library(zoo)
library(forecast)
library(dynlm)


df <- read.csv('hw3_data.csv')
```

### To-DO
### Redo ARMA model, look for solutions for dynlm model (works on other end but not my own --> check packages)

```{r}
# Set the start date
start_date <- mdy("01/01/2023")

# Generate a sequence of dates
dates <- seq(start_date, by = "day", length.out = 200)

# Create a time series object
ts_data <- ts(data = df$y, start = start_date, frequency = 365)

# Create a data frame of the time series to use in line plot
ts_df <- data.frame(Date = dates, Value = df$y, x = df$x)


```

```{r}
ggplot(data = ts_df, aes(x = Date, y = Value)) +
  geom_line() +
  labs(x = "Date", y = "Value", title = "Time Series Line Plot")
```

In this series, we can see that after each time the Y values peaks, there is a steep drop-off/crash that occurs, and after each one the y value rebounds but not nearly to the extent of the previous peak. The mean Y value in this series is equal to around 6.633


```{r}
# Ljung-Box Test for white noise
ljung_box <- Box.test(ts_data, lag = 20, type = "Ljung-Box")
print(ljung_box)
```

```{r}
values <- ts_data

# Create ACF plot
ggplot(data = data.frame(lag = 0:20, acf = acf(values, lag.max = 20, plot = FALSE)$acf), aes(x = lag, y = acf)) +
  geom_bar(stat = "identity") +
  labs(x = "Lag", y = "Autocorrelation", title = "Autocorrelation Function (ACF) Plot")

```

```{r}
# Calculate PACF values
pacf_values <- pacf(values, lag.max = 20, plot = FALSE)$acf

# Create PACF plot
ggplot(data = data.frame(lag = 1:length(pacf_values), pacf = pacf_values), aes(x = lag, y = pacf)) +
  geom_bar(stat = "identity") +
  labs(x = "Lag", y = "Partial Autocorrelation", title = "Partial Autocorrelation Function (PACF) Plot")
```


```{r}
acf(ts_data)
```




```{r}
arima_model <- 

plot(arima_model$residuals)
```


```{r}
Box.test(arima_model$residuals, lag = 20, type = "Ljung-Box")

```
Since there is no clear pattern shown in the residual plot for our ARMA model, as well as our p-value in the Box-Ljung test on the residuals of the model not being significant, we can assume the ARMA model fits our time series


```{r}
model1 <- dynlm::dynlm(Value ~ lag(Value, 1) + lag(Value, 2) + x, data = ts_df)

model2 <- dynlm(Value ~ L(Value, 1) + L(Value, 2) + x, data = ts_df)


summary(model2)$r.squared

class(ts_df$Date)
```




```{r}
plot(model$residuals)
```

I'm unsure of where exactly I may have gone wrong, but it looks as though my model is unreliable. In this case, I tried to include a few lags which I saw both my ACF and PACF plots peaked as these lags suggested there was some form of autocorrelation and I wanted my model to account for them, however it seems from looking at the plot of the model's residuals that these values follow a pattern and suggest that this model does not in fact fit our time series. 














